### 2018-05-01 Paper/jaccardbaetica.tex
add new pic

Our case study examines the relation between the distribution of amphoric stamps and the workshops. The workshops were situated in different locations in Baetica province, along the river Guadalquivir and its tributary Genil in order to detect similarities between stamps from workshops and spatial distance.

@@

Neither it seems that stamps were used to specify the quality or value of the product \citep{callender}. Probably our results could be interpreted due to several reason according to previous hypotheses. The use of these amphoric stamps could be exclusively running by the owner or families to distinguish the amphora workshop (CITAR).

(aumentar)
On the other hand, it can be interpreted somehow a batch systematic organization to prepare and distribute the commodity considering that Dressel 20 type was not marked in several cases (CITAR)
it could be somehow a batch systematic organization to prepare and distribute the commodity, considering that Dressel 20 was not marked in several cases. This method was used of counting BLA BAL

>>>>

Our case study examines the relation between the distribution of amphoric stamps and the workshops. The workshops were situated in different locations in Baetica province, along the river Guadalquivir and its tributary Genil in order to detect similarities between stamps from workshops and spatial distance (see Fig.\ref{workshop})

\begin{figure}[htp]
	\centering
\includegraphics[width=\linewidth]{figs/workshop}
\caption{Distribution of the workshops}
\label{workshop}
\end{figure}

@@

 Probably our results could be interpreted due to several reason according to previous hypotheses.

On the one hand, the use of these amphoric stamps could have been exclusively running by the owner of families to distinguisth the amphora workshop (CITAR). The kind of distintion does not seem to be used to specify the quality or value of the product \citep{callender}. 
On the other hand, it can be interpreted somehow a batch systematic organization (CITAR). Considering that Dressel 20 was not marked in several cases (CITAR), some authors point out that potters marked amphorae to prepare and distribute the commodity to be shipped. This method would be used as an identifier to count the number of amphorae of a banch (CITAR). This is would be explain why we found different stamps in a same workshops.
